Anonymous provision of services via blockchain

### 2022-03-09 access.tex
proof reading

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}
\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Anonymous provision of services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski}\authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information. This situation exposes customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a protocol for coordinating anonymous service provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
A service provider can employ our protocol to provide services without collecting personal information. Possible applications for this protocol include anonymous clinical drugs, steroids, parenting testing, or anonymous legal advice.
In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, payment with cash, and a decentralized conflict resolution system.
Our protocol may enable various services currently based on unacceptable trust assumptions to the SP.
\end{abstract}

@@

\maketitle
\section{Introduction}
Service providers (SP) like lawyers, laboratories, auditors, or banks,
to provide services, require data that is often associated with the user
identity.

@@

Such user information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or
commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.

Important individuals like top government, influencers, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

@@

It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SP and less responsibility borne by SP.

@@

Our protocol allows taking such tests anonymously, therefore eliminating the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

@@

Our protocol would allow taking such advice anonymously, therefore eliminating the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

@@

To achieve these objectives, we use:
\begin{itemize}
    \item Privacy-preserving blockchain, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party.
    \item Content-addressable peer-to-peer storage network to provide results to customers. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption: to encrypt and decrypt results published on public networks.
        \item Digital signatures: To achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted-third party but decentralized blockchain and
distributed content-addressable storage network.

@@

\begin{itemize}
\item Anonymity:
throughout the whole transaction, the customer stays anonymous to all external observers.
\item Fairness:
at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in the worst position.
\item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the building blocks related to fair exchanges, blockchain, anonymity and confidentiality, and storage network. 
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by
introducing online trusted third parties that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take
a product from a source cabinet and provide it to a destination cabinet.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the source cabinet.
    \item Delivery agent collects the product from the source cabinet and posts it to the delivery cabinet.
    \item Customer collects the product from the delivery cabinet using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the delivery cabinet and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

@@

\begin{itemize}
    \item the TTP does not misbehave or collude with any party. 
    \item The customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished.   
    \item All banks maintain a global list of coins' serial numbers to prevent double-spending problems. 
    \item The source cabinet and delivery cabinet exist, and in both, the product access is protected by a password.
    \item Delivery cabinet is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute. 
    \item There exists a trusted delivery agent.
    \item Communication channels between parties provide anonymity.
\end{itemize}

@@

Themis~\cite{meng2019themis} is a fair exchange
protocol that uses blockchain instead of TTP. It provides an escrow
service for secure exchanging cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

@@

However, since the system uses Ethereum— fully traceable blockchain—its anonymity is achieved as long as the addresses are not identified with the real identities, which we call pseudonymity rather than anonymity (see Section~\ref{sec:pseudo-anon}). Also, the protocol does not cover the dispute between the parties.

@@

Nevertheless, the blockchain paradigm has its limitations. Blockchain can assure the correctness of data existing only on the blockchain—the problem arises in the contact between blockchain and the real world when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.

@@

Possible directions toward semi-autonomous decentralized resolution
system are discussed in Section ~\ref{sec:future-work}.

@@

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantageous position; therefore, he has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in Section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further Section~\ref{payment-for-services}.

@@

\subsection{Message Board}\label{message-board}
The proof-of-provision that we coined for the purpose of this protocol
is generally called the proof-of-existence
\cite{proofofexistence, de2016stampery, Chainpoi39}.

The idea behind proof-of-existence is to certify that some information
has existed at a certain moment, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
non-repudiation requirement).

We need this functionality for two reasons: (1) Communicate the existence
of the result to the customer to whom the SP have no other
communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.

@@

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved} or message board~\cite{hinarejos2019solution} or trusted timestamping~\cite{gipp2015decentralized}. In this work, we call it a message board.

@@

Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}. For our work, we rely on more concrete definitions, i.e.~confidentality, and anonymity.

Confidentiality is the ability to hide the details of action from others. Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.

@@

Some systems guarantee pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identity behind the pseudonym. Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

@@

Depending on the cryptocurrency, the link can be created in different
ways:

\item
  separate address — each transaction derives a new address uniquely
  associated with the transaction. Such addresses can be derived
  using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
\item
  memo — the payments are sent to one SP account but contain an extra
  field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is
  considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}

\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}
\newcommand\sbullet[1][.75]{\mathbin{\ThisStyle{\vcenter{\hbox{%
  \scalebox{#1}{$\SavedStyle\bullet$}}}}}%
}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2017.DOI}

\title{Anonymous provision of services via blockchain}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information. This situation exposes customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a protocol for coordinating anonymous service provision. Our proposal uses blockchain for both anonymous payments and proofs of existence (so-called message board) and content-addressable network (e.g.~IPFS) for results delivery.
A service provider can employ our protocol to provide services without collecting personal information. Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
In case of dispute, either due to exceeding deadlines or providing incorrect results, the customer can disclose the whole interaction and prove to justice (police or court) the misbehaviour of the service provider.
We analyze the protocol in the context of fairness and discuss further extensions to an anonymous delivery system, payment with cash, and a decentralized conflict resolution system.
Our protocol may enable various services currently based on unacceptable trust assumptions to the service providers.
\end{abstract}

@@

\maketitle
\section{Introduction}
Service providers (SPs) like lawyers, laboratories, auditors, or banks,
to provide services, require data that is often associated with the user
identity.

@@

Such personal information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smith2011information}.

Important individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

@@

It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SPs and less responsibility borne by SPs.

@@

Our protocol allows taking such tests anonymously, eliminating the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

@@

Our protocol would allow taking such advice anonymously, eliminating the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

@@

To achieve these objectives, we use:
\begin{itemize}
    \item Privacy-preserving cryptocurrency, to allow customers anonymously pay for the services.
    \item Message board blockchain, to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Content-addressable peer-to-peer storage network to provide results to customers. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
We contribute to the field of fair exchanges by proposing a simple, practical, and anonymous protocol that does not rely on the centralized trusted third party but decentralized blockchain and
distributed content-addressable storage network.

@@

\begin{itemize}
\item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
\item Fairness:
at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
\item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.

@@

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we briefly review related works. 
Section~\ref{sec:building-blocks} explains the building blocks of fair exchanges, blockchain, storage network, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
Section~\ref{sec:future-work} discuss possible improvements. 
Finally, section~\ref{sec:conclusion} concludes the paper.

@@

Authors of~\cite{birjoveanu2015anonymity} proposed a
fair exchange of physical products and electronic payment protocol that
guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide
fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from a SC and provide it to a DC.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant.

@@

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the SC.
    \item Delivery agent collects the product from the SC and posts it to the DC.
    \item Customer collects the product from the DC using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the DC and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

@@

\begin{itemize}
    \item the TTP does not misbehave or collude with any party;
    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item the SC and DC exist, and in both, the product access is protected by a password;
    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
    \item there exists a trusted delivery agent;
    \item communication channels between parties provide anonymity.
\end{itemize}

@@

Themis~\cite{meng2019themis} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

@@

However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

@@

Nevertheless, the blockchain paradigm has its limitations. Blockchain can assure the correctness of data existing only on the blockchain. The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized.

@@

Possible directions toward semi-autonomous decentralized resolution system are discussed in section ~\ref{sec:future-work}.

@@

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, he has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

@@

\begin{enumerate}
    \item Proof of delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.

@@

\subsection{Message Board}\label{message-board}
The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence
\cite{proofofexistence, de2016stampery, Chainpoi39}.

The idea behind proof of existence is to certify that some information
has existed at a certain moment, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
non-repudiation requirement).

We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP have no other communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.

@@

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbach2015improved}, trusted timestamping~\cite{gipp2015decentralized}, or message board~\cite{hinarejos2019solution}. In this work, we call it a message board.

@@

Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smith2011information}. For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.

Confidentiality is the ability to hide the details of an action from others. Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.

@@

Some systems guarantee pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identity behind the pseudonyms. Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

@@

Depending on the cryptocurrency, the link can be created in different
ways:
% continue reading from here
\begin{itemize}

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)~\cite{bipsbip089}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}
